---
title: "2DGraph_Gating"
author: "CB"
date: "2023-02-22"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

# All Libraries
```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(ggrepel)
library(ggpubr)
library(tidyverse)
library(matrixStats)
library(hrbrthemes)
library(viridis)
library(plotly)
```


# Global data

MatrixLib is the entire library of the human transmembrane proteins 
Newrow is used to organized the all of the gates in order
  number of gates in data (Change if needed)

```{r}
MatrixLib <- read_csv("GitHub/MPA-DataAnalisys/Screen_Analysis/MatrixLib/MatrixLib.csv") %>%
             select(symbol_raw, symbol, matrix_col, matrix_row)

newrow <- c(1:23)
```

## All CSV data from one file

```{r}

data_files <- list.files("~/GitHub/MPA-DNA-tool/Gating/Dataset/Growth_Control")  # Identify file names
data_files

for(i in 1:length(data_files)) {                              # Head of for-loop
  assign(paste0("data", i),                                   # Read and store data frames
         read_csv(paste0("~/GitHub/MPA-DNA-tool/Gating/Dataset/Growth_Control/",
                         data_files[i]), skip = 1))
}
```

# Data select
Here I select the data to process from all of the csvs that has been uploaded.
Mainly for easy access to several datasets 

```{r}

allgates_onlycontrol <- data3 %>% 
  slice(342) %>% 
  select(-(1:2))

allgates_all <- data3 %>% 
  select(-2)

allgates_allavg <- data3 %>% 
  select(-(1:2))

```

# Process the data 



```{r}

allgates_onlycontrol <- rbind(allgates_onlycontrol, newrow)
allgates_onlycontrol <- as.data.frame(t(allgates_onlycontrol)) %>%
                        select(Cntr2 = 1, Gates = 2)

speedGrowth_onlycontrol <- abs(diff(allgates_onlycontrol$Cntr2))
speedGrowth_onlycontrol <- cbind(newrow, speedGrowth_onlycontrol)
speedGrowth_onlycontrol <- data.frame(speedGrowth_onlycontrol) %>%
                           select(GatesD = 1, Diff2 = 2) %>% 
                           slice(-23) 

    # - Processing data for all gates with the average
allgates_all1 <- data.frame(colMeans(allgates_allavg[sapply(allgates_allavg, is.numeric)], na.rm = TRUE)) %>% 
  rename(MeansGates = 1 )

allgates_all1$SDGates <- sapply(allgates_allavg, sd, na.rm = TRUE)

allgates_all1 <- cbind(allgates_all1, newrow)

    # - Speed Growth for AVG
newrow1 <- c(1:22)

allgates_all2 <- abs(diff(allgates_all1$MeansGates))

allgates_all2 <- cbind(newrow1, allgates_all2)

allgates_all2 <- data.frame(allgates_all2) %>%
  select(GatesD = 1, Diff = 2)
```
# Plot - Gate Change
Graphs that looks at the % of 648AF in all cells per gate
  Fig.A - Conciders only the Dummy cells
  Fig.B - Looks at the change per gate of Fig.A
  Fig.C - Conciders the average of all wells
  Fig.D - Looks at the change per gate of Fig.C
  

```{r}

ag_oc <- ggplot(allgates_onlycontrol, aes(x=Gates)) + 
  geom_line(aes(y = Cntr2), color = "#000000", size = 1) + 
  xlab("Gates") + ylab("Growth")

sG_oc <- ggplot(speedGrowth_onlycontrol, aes(x=GatesD)) + 
  geom_line(aes(y = Diff2), color = "#000000", size = 1) + 
  xlab("Gates") + ylab("Speed Growth")

aG_awells <- ggplot(allgates_all1, aes(x=newrow)) + 
  geom_line(aes(y = MeansGates), color = "#000000", size = 1.1) + 
  geom_errorbar(aes(ymin = MeansGates-SDGates, ymax = MeansGates+SDGates), color = "#000000", width=.5) +
  geom_point(aes(y = MeansGates), size=2, shape=21, fill="white") + 
  xlab("Gates") + ylab("Avg Growth")

sG_awells <- ggplot(allgates_all2, aes(x=GatesD)) + 
  geom_line(aes(y = Diff), color = "#000000", size = 1) + 
  xlab("Gates") + ylab("Speed Growth")



ggarrange(ag_oc, sG_oc, aG_awells, sG_awells, 
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2)
```

Recomended Gates

Calculates and selects a range of gates 

```{r}


# - Recommended Gates


while (sum(speedGrowth_onlycontrol$Diff2) > 0.001) {
speedGrowth_onlycontrol <- speedGrowth_onlycontrol %>% slice(-1)
}

RecGates <- speedGrowth_onlycontrol %>% slice(1) %>% select(1)

#RecGates <- filter(speedGrowth_onlycontrol,
#                   Diff2 <= 0.001) %>% 
#  slice(1) %>% 
#  select(1)

while (sum(allgates_all2$Diff) > .1) {
  allgates_all2 <- allgates_all2 %>% slice(-1)
}

RecGates_all <- allgates_all2 %>% slice(1) %>% 
  select(1)

#RecGates_all <- filter(allgates_all2,
#                   Diff <= 0.01) %>% 
#  slice(1) %>% 
#  select(1)


RecGates_all[nrow(RecGates_all) + 1,] <- RecGates

GateNumber <- ceiling(mean(RecGates_all$GatesD))

GateNumberD <- c(GateNumber, GateNumber + 1) #change to + 0, +1
GateNumberU <- c(GateNumber + 4, GateNumber + 5) #change to + 4, +5


SelectedGates <- allgates_all %>% 
  select(1, GateNumberD + 1, GateNumberU + 1) %>% 
  slice(-344)

```

# 2D Graph





```{r}


# - 2D Graph
  # - Process 2D Graph
for(i in 1:4){
  colnames(SelectedGates)[i+1] = paste0("gate", i) 
}

for(i in 1:4){
  SelectedGates[[paste0('S_N', i)]] <- SelectedGates[[paste0("gate", i)]] / mean(SelectedGates[[paste0("gate", i)]], trim = 0.1)
}

SelectedGates <- SelectedGates %>% select(-(2:5))

SelectedGates2 <- MatrixLib %>%
  inner_join(SelectedGates,
             by = c("matrix_row" = "Well ID")) %>% 
  inner_join(SelectedGates,
             by = c("matrix_col" = "Well ID"))

for(i in 1:4){
  colnames(SelectedGates2)[i+4] = paste0("S_N", i, ".y") 
  colnames(SelectedGates2)[i+8] = paste0("S_N", i, ".x") 
}


SelectedGates2$S_N.y <-  rowMeans(SelectedGates2[,5:8])
SelectedGates2$S_N.x <-  rowMeans(SelectedGates2[,9:12])

AvgSelectedGate <- SelectedGates2 %>% select(1:4, 13, 14)



# - Spike wells

AbvAvg <- sum(sd(AvgSelectedGate$S_N.y), sd(AvgSelectedGate$S_N.x)) / 2

if (AvgSelectedGate[999,5] > 10 || AvgSelectedGate[999,6] > 10 ) {
  Spikewell <- max(AvgSelectedGate[999,5:6]) * 2 / min(AvgSelectedGate[999,5:6]) 
  AvgSelectedGate[, 5:6] [AvgSelectedGate[, 5:6] == min(AvgSelectedGate[999,5:6])] <- 2 + AbvAvg *3
  AvgSelectedGate[, 5:6] [AvgSelectedGate[, 5:6] == max(AvgSelectedGate[999,5:6])] <- Spikewell + AbvAvg *3
}


if (AvgSelectedGate[1999,5] > 10 || AvgSelectedGate[1999,6] > 10 ) {
  Spikewell <- max(AvgSelectedGate[1999,5:6]) * 2 / min(AvgSelectedGate[1999,5:6]) 
  AvgSelectedGate[, 5:6] [AvgSelectedGate[, 5:6] == min(AvgSelectedGate[1999,5:6])] <- 2 + AbvAvg *3
  AvgSelectedGate[, 5:6] [AvgSelectedGate[, 5:6] == max(AvgSelectedGate[1999,5:6])] <- Spikewell + AbvAvg *3
}

if (AvgSelectedGate[2999,5] > 10 || AvgSelectedGate[2999,6] > 10 ) {
  Spikewell <- max(AvgSelectedGate[2999,5:6]) * 2 / min(AvgSelectedGate[2999,5:6]) 
  AvgSelectedGate[, 5:6] [AvgSelectedGate[, 5:6] == min(AvgSelectedGate[2999,5:6])] <- 2 + AbvAvg *3
  AvgSelectedGate[, 5:6] [AvgSelectedGate[, 5:6] == max(AvgSelectedGate[2999,5:6])] <- Spikewell + AbvAvg *3
}

if (AvgSelectedGate[3999,5] > 10 || AvgSelectedGate[3999,6] > 10 ) {
  Spikewell <- max(AvgSelectedGate[3999,5:6]) * 2 / min(AvgSelectedGate[3999,5:6]) 
  AvgSelectedGate[, 5:6] [AvgSelectedGate[, 5:6] == min(AvgSelectedGate[3999,5:6])] <- 2 + AbvAvg *3
  AvgSelectedGate[, 5:6] [AvgSelectedGate[, 5:6] == max(AvgSelectedGate[3999,5:6])] <- Spikewell + AbvAvg *3
}

if (AvgSelectedGate[4999,5] > 10 || AvgSelectedGate[4999,6] > 10 ) {
  Spikewell <- max(AvgSelectedGate[4999,5:6]) * 2 / min(AvgSelectedGate[4999,5:6]) 
  AvgSelectedGate[, 5:6] [AvgSelectedGate[, 5:6] == min(AvgSelectedGate[4999,5:6])] <- 2 + AbvAvg *3
  AvgSelectedGate[, 5:6] [AvgSelectedGate[, 5:6] == max(AvgSelectedGate[4999,5:6])] <- Spikewell + AbvAvg *3
}

if (AvgSelectedGate[5999,5] > 10 || AvgSelectedGate[5999,6] > 10 ) {
  Spikewell <- max(AvgSelectedGate[5999,5:6]) * 2 / min(AvgSelectedGate[5999,5:6]) 
  AvgSelectedGate[, 5:6] [AvgSelectedGate[, 5:6] == min(AvgSelectedGate[5999,5:6])] <- 2 + AbvAvg *3
  AvgSelectedGate[, 5:6] [AvgSelectedGate[, 5:6] == max(AvgSelectedGate[5999,5:6])] <- Spikewell + AbvAvg *3
}


  # - Define SD Threshold

  # - Simple 2D Graph



##### Analysis - 2D Scatter Plot #####

x <- 2.5  # STD Multiplier 

rm(Manual_SD)


Threshold.y <- sd(AvgSelectedGate$S_N.y) * x + mean(AvgSelectedGate$S_N.y, trim = 0.1)  
Threshold.x <- sd(AvgSelectedGate$S_N.x) * x + mean(AvgSelectedGate$S_N.x, trim = 0.1)

options(ggrepel.max.overlaps = Inf)

theplot = ggplot(AvgSelectedGate, aes(x=S_N.x, y=S_N.y, label=symbol)) + 
  geom_label_repel(aes(label = ifelse(S_N.y>Threshold.y & S_N.x>Threshold.x, as.character(symbol),'')),
                   box.padding   = 1.35, 
                   point.padding = 1.5,
                   segment.color = 'grey50')  +
  geom_point(color = dplyr::case_when(AvgSelectedGate$S_N.y > Threshold.y & AvgSelectedGate$S_N.x > Threshold.x ~ 
                                        "#d95f02", TRUE ~ 
                                        "#7570b3"), 
             size = dplyr::case_when(AvgSelectedGate$S_N.y > Threshold.y & AvgSelectedGate$S_N.x > Threshold.x ~ 
                                       4, TRUE ~ 
                                       2), 
             alpha = dplyr::case_when(AvgSelectedGate$S_N.y > Threshold.y & AvgSelectedGate$S_N.x > Threshold.x ~ 
                                        1, TRUE ~ 
                                        .2))  +
  geom_vline(aes(xintercept = Threshold.x),
             color="blue", 
             linetype="dashed", 
             size=1,
             alpha = .5) +
geom_hline(aes(yintercept = Threshold.y),
           color="blue", 
           linetype="dashed", 
           size=1,
           alpha = .5)

theplot


```

# - In depth Hits


```{r}

  # - In depth Hits
  
Manual_SD <- filter(SelectedGates2, 
                     S_N.y >= sd(SelectedGates2$S_N.y) * x + mean(SelectedGates2$S_N.y, trim = 0.1) & 
                       S_N.x >= sd(SelectedGates2$S_N.x) * x + mean(SelectedGates2$S_N.x, trim = 0.1))




Manual_SD <- transform(Manual_SD, row_stdev=apply(Manual_SD, 1, sd, na.rm=TRUE))

ggplot(data = Manual_SD, aes(x=S_N.x, y=S_N.y, size = row_stdev, color=symbol), color = 'blue') + 
  geom_point(alpha=0.7) +
  scale_size(range = c(4, 15), name="SD") +
  scale_fill_viridis(discrete=TRUE, guide=FALSE, option="A") +
  theme_ipsum() +
  geom_label_repel(aes(label = as.character(symbol), size = 1), force = 10) +
  theme(legend.position = "none") +
  geom_segment(aes(x=S_N.x, y=S_N.y, xend=S_N4.x-x, yend=S_N4.y-x), 
               arrow = arrow(length=unit(.5, 'cm')), 
               size = .5)
```

